A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2016-06-09 LensingPaper_draft_v4.01.tex
Edited section on merger slightly.

%--------------------------------------------
We have presented different dynamical models for the central region of J1331. Some of them capture the observed kinematics, but none of them work at both small and large radii. In the following we discuss possible reasons, also by comparing our results to previous work.
%--------------------------------------------

@@

%--------------------------------------------
\subsection{On J1331's possible merger history and modelling failures}
%--------------------------------------------

Even though investigation of the photometry of J1331 did not reveal a distinct blue core in J1331, we cannot fully exclude the possibility that J1331 has such a $\Upsilon_*$ gradient (see discussion in Sections \ref{sec:results_JAM_SB_MfL} and \ref{sec:results_JAM_SB_gradient}). In this case the restrictive assumption of a constant $\Upsilon_*$ in our JAM modelling could have lead to wrong conclusions about the DM distribution.

Another way how galaxy encounters can modify the structure of galaxies is the excitation of warps \citep{1991wdir.book.....C,2013pss5.book..923S}. Warps lead to a twist in the projected kinematic major axis with radius, which is then also misaligned with the photometric major axis (\citealt{1998gaas.book.....B}, \S 8.2.4). From kinematics along the photometric major axis only it cannot be determined if such a twist or misalignment is present in J1331. But if it were, our modelling assumption of axisymmetry would not be satisfied anymore.

We note that kinematics measured along an axis different from the kinematic major axis would result in $v_\text{rot}$ measurements being lower than the actual maximum $v_\text{circ}$. At large radii this could lead to an underestimation of the DM halo mass.
%--------------------------------------------

>>>>

%--------------------------------------------
We have presented different dynamical models for the central region of J1331. Some of them capture the observed kinematics, but none of them work at both small and large radii. \NEW{In the following we try to resolve some of the ambiguities by discussing possible reasons, by comparing our results to previous work and by venturing some guesses on the true nature of J1331's matter distribution, which should be easily testable by future observations.}\OLD{In the following we discuss possible reasons, also by comparing our results to previous work.}
%--------------------------------------------

%--------------------------------------------
\subsection{On J1331's possible merger history\OLD{ and modelling failures}}
%--------------------------------------------
\NOTE{[This subsection was moved from a later position to the beginning of this section.]}

Even though investigation of the photometry of J1331 did not reveal a distinct blue core in J1331, we cannot fully exclude the possibility that J1331 has such a $\Upsilon_*$ gradient (see discussion in Sections \ref{sec:results_JAM_SB_MfL} and \ref{sec:results_JAM_SB_gradient}). \NEW{Stellar population analysis with spectra taken at different positions within the bulge could provide further information on the true $\Upsilon_*(R')$.}\OLD{In this case the restrictive assumption of a constant $\Upsilon_*$ in our JAM modelling could have lead to wrong conclusions about the DM distribution.}

Another way how galaxy encounters can modify the structure of galaxies is the excitation of warps \citep{1991wdir.book.....C,2013pss5.book..923S}. Warps lead to a twist in the projected kinematic major axis with radius, which is then also misaligned with the photometric major axis (\citealt{1998gaas.book.....B}, \S 8.2.4). From kinematics along the photometric major axis only it cannot be determined if such a twist or misalignment is present in J1331\NEW{, but it should be immediately visible in a 2D kinematic map}.\OLD{ But if it were, our modelling assumption of axisymmetry would not be satisfied anymore.}
\Wilma{[TO DO: Mention that warps would require other modelling techniques than the axisymmetric Jeans models.]}

\Wilma{[More: "We note that kinematics measured along an axis different from the kinematic major axis would result in $v_\text{rot}$ measurements being lower than the actual maximum $v_\text{circ}$. At large radii this could lead to an underestimation of the DM halo mass." somewhere else.]}
%--------------------------------------------

@@
